### 2023-06-29 paper/main.tex
spectra_added

\section{Comparison with direct modal bandlimitation}
\begin{figure*}[h!]
    \begin{center}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center2.png}
            \footnotesize \put(0,2){(a)}
            \footnotesize \put(45,102){Center}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_left2.png}
            \footnotesize \put(0,2){(b)}
            \footnotesize \put(45,102){Left}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
            \footnotesize \put(0,2){(c)}
            \footnotesize \put(45,102){Front}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
            \footnotesize \put(45,102){Back}
        \end{overpic}\\  \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
            \footnotesize \put(0,2){(e)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_left.png}
            \footnotesize \put(0,2){(f)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
            \footnotesize \put(0,2){(g)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_back.png}
            \footnotesize \put(0,2){(h)}
        \end{overpic}\\ \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
            \footnotesize \put(0,2){(i)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_left.png}
            \footnotesize \put(0,2){(j)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(k)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_back.png}
            \footnotesize \put(0,2){(l)}
        \end{overpic}\\
    \end{center}
    \caption{Comparison of the proposed, temporal filtering-based LWFS approach with direct modal bandlimitation.
    First row (a-d) depicts the synthesized field with temporal LWFS, Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
    \label{Fig:comparison}
\end{figure*}

@@

The two methods are compared via the exemplary synthesis scenario discussed in the foregoing, synthesizing an impulsive plane wave, by bandlimiting the driving functions to the Nyquist wavenumber.
The result of synthesis is investigated for four different reference positions:
\begin{itemize}
    \item Center: $\vxref = \left[0,0,0\right]^{\mathrm{T}}$
    \item Left: $\vxref = \left[0,1,0\right]^{\mathrm{T}}$
    \item Back: $\vxref = \left[-1,0,0\right]^{\mathrm{T}}$
    \item Front: $\vxref = \left[1,0,0\right]^{\mathrm{T}}$
\end{itemize}
Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches, each column illustrating a different reference position.
The first row (a-d) shows the synthesized field at the time instant of the plane wave pass-by through the reference position by implementing the proposed LWFS approach, with the second row (e-h) depicting the same result with using modal bandlimitation. 
The third row illustrates the measured frequency response of the synthesized fields at the reference positions.

@@

The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.

>>>>

\section{Comparison with direct modal bandlimitation}

\begin{figure}[]
    \begin{center}
        \begin{overpic}[width = 0.75\columnwidth]{figs/nara_spectrum_center.png}
            \footnotesize \put(0,2){(a)}
        \end{overpic}
        \\
        \begin{overpic}[width = 0.75\columnwidth]{figs/nara_spectrum_left.png}
            \footnotesize \put(0,0){(b)}
        \end{overpic}
    \end{center}
    \caption{Spectrum of LWFS driving functions by direct modal bandlimitation with the reference position choosen at the center, $\vxref = \left[0,0,0\right]^{\mathrm{T}}$ (a) and on the left side, $\vxref = \left[0,1,0\right]^{\mathrm{T}}$ (b).
    }
    \label{Fig:nara_spectrum}
\end{figure}

\begin{figure*}[]
    \begin{center}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center2.png}
            \footnotesize \put(0,2){(a)}
            \footnotesize \put(45,102){Center}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_left2.png}
            \footnotesize \put(0,2){(b)}
            \footnotesize \put(45,102){Left}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
            \footnotesize \put(0,2){(c)}
            \footnotesize \put(45,102){Front}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
            \footnotesize \put(45,102){Back}
        \end{overpic}\\  \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
            \footnotesize \put(0,2){(e)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_left.png}
            \footnotesize \put(0,2){(f)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
            \footnotesize \put(0,2){(g)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_back.png}
            \footnotesize \put(0,2){(h)}
        \end{overpic}\\ \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
            \footnotesize \put(0,2){(i)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_left.png}
            \footnotesize \put(0,2){(j)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(k)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_back.png}
            \footnotesize \put(0,2){(l)}
        \end{overpic}\\
    \end{center}
    \caption{Comparison of the proposed, temporal filtering-based LWFS approach with direct modal bandlimitation.
    First row (a-d) depicts the synthesized field with temporal LWFS, Second row (e-h) depicts the synthesized field with modal bandlimitation and third row (i-l) compares the frequency response at the reference position.}
    \label{Fig:comparison}
\end{figure*}

@@

The two methods are compared via the exemplary synthesis scenario discussed in the foregoing, synthesizing an impulsive plane wave, by bandlimiting the driving functions to the Nyquist wavenumber.
The result of synthesis is investigated for four different reference positions:
\begin{itemize}
    \item Center: $\vxref = \left[0,0,0\right]^{\mathrm{T}}$
    \item Left: $\vxref = \left[0,1,0\right]^{\mathrm{T}}$
    \item Back: $\vxref = \left[-1,0,0\right]^{\mathrm{T}}$
    \item Front: $\vxref = \left[1,0,0\right]^{\mathrm{T}}$
\end{itemize}

For the central and the left reference positions first the spectra of the driving functions were investigated.
Figure \ref{Fig:nara_spectrum} already reflects the fact that the proposed temporal LWFS approach is an approximation of the reference solution, i.e. of the direct modal bandlimitation.
It is verified that modal bandlimitation LWFS performs the same "steering" of the modal spectrum into the direction of the central wavenumber, realizing a freuqency dependent spatial band-pass filter.

Figure \ref{Fig:comparison} presents the comparison of the result of the two approaches via the synthesized field and the frequency response, each column illustrating a different reference position.
The first row (a-d) shows the synthesized field at the time instant of the plane wave pass-by through the reference position by implementing the proposed LWFS approach, with the second row (e-h) depicting the same result with using modal bandlimitation. 
The third row illustrates the measured frequency response of the synthesized fields at the reference positions.

@@

The present contribution discussed a novel local Wave Field Synthesis approach, relying on a filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.

It was demonstrated via numerical simulations that the approach is capable of the suppression of aliasing wavefronts along a straight line/ray (containing the reference position) with its direction of adjusted by the center wavenumber of the antialiasing spatial band-pass filter.
The performance of the presetned approach was compared with LWFS by direct modal bandlimitation as a direct, reference solution.
It was shown, that temporal LWFS gives a feasible approximation for the reference, while being a more robust approach, with less computational demand, allowing real-time implementations.
